---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
  
```{r}
read.csv("activity.csv") -> mydata
head(mydata)
tail(mydata)
```
  
## What is mean total number of steps taken per day?
Calculate the total number of steps taken per day
```{r}
aggregate(mydata$steps,by=list(mydata$date),function(x) mean(x,na.rm=TRUE)) -> dtx
```
Make a histogram of the total number of steps taken each day
```{r, echo =TRUE}
hist(dtx$x,main="Histogram of the total number of steps taken each day",xlab="Mean")
```



Calculate and report the mean and median of the total number of steps taken per day
```{r}
aggregate(mydata$steps,by=list(mydata$date),function(x) median(x,na.rm=TRUE)) -> dtx2
data.frame(meanx = mean(dtx$x,na.rm=TRUE),medianx = median(dtx$x,na.rm=TRUE))
```

## What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo =TRUE}
plot.ts(dtx$x,type="l")
```


## Imputing missing values
Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
mydata$steps -> st1
length(st1[is.na(st1)])
```


## Are there differences in activity patterns between weekdays and weekends?

